
%\cvsection{Honors \& Awards}
%\begin{itemize}
 %  \item Received Best Debut Award at Atos.
  %  \item Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.
   % \item Awarded with Narotam Sekhsaria Foundation Scholarship
%\end{itemize}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}
\cvsection{Education}
\cvevent{B.S. in Computer Science}{Rensselaer Polytechnic Institute}{Sep '19 -- May '23}{Troy, NY}
\begin{itemize}
\item GPA: 3.34/4.0
\item Courses: Data Structures, Fund. of CS, Computer Organization, Intro to Algo., Software Documentation \& Design, Principles of Software.
\end{itemize}
% \smallskip
% \cvproject{}
\cvsection{Leadership}

\cvevent{Executive Board Social Chair}{RPI Philippine American League}{Jan '21 -- May '21}{Troy, NY}
\begin{itemize}
\item Participated in weekly executive board meetings to discuss club status, develop future plans, and reflect on accomplished material.
\item Created club-wide activities for general body meetings of 20+ participants.
\item Organized intercollegiate event of 30 participants between Filipino culture clubs.
\end{itemize}
% \smallskip

% \cvproject{}
\cvsection{Projects}
\cvproject{FakeBlock}
\begin{itemize}
\item A deepfake detection browser-extension made with TypeScript and Tensorflow.
\item Worked in a 4-man team using Scrum methodology.
\item Created script for injecting collapsible DOM elements into websites.
\item Designed dynamic results page UI with React and material-ui.
\item Wrote unit tests with TS-Jest.
\end{itemize}
% \smallskip

% \divider

\cvproject{Ongatchi - Tamagotchi that eats your music}
\begin{itemize}
\item Created minimalistic GUI in Python with Tkinter library.
\item Implemented Last.fm API to track users’ music listening history.
\end{itemize}
% \smallskip

% \divider

\cvproject{wav-art}
\begin{itemize}
\item Created generative art by processing .wav files in Python.
\item Used pydub library to create normalized data points from soundwaves.
\item Plotted data using a modular cellular automata algorithm and matplotlib.
\end{itemize}

% \cvproject{}
\cvsection{SKILLS AND TOOLS}
% \cvskill{MS Office, MS Project}{}
\begin{itemize}
    \item \textbf{Languages:} Python, TypeScript, JavaScript, C/C++, Dart, Java
    \item \textbf{Tools:} Git, Flutter, Amazon Mechanical Turk, Jupyter Notebook
\end{itemize}